---
title: "Clark-Izzi-ADA-homework-1"
output: html_document
---

Challenge 1:

```{r}
quote <- "There is grandeur in this view of life, with its several powers, having been originally breathed by the Creator into a few forms or into one; and that, whilst this planet has gone circling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being evolved."

split_quote <- strsplit(quote, " ")

every_fourth <- split_quote[[1]][seq(from = 4, to = 60, by = 4)]
print(every_fourth)
every_fourth <- sort(every_fourth, decreasing = TRUE)
print(every_fourth)
```

Challenge 2:

```{r}
m1 <- matrix(
  data = seq(from = 1, to = 159, by = 2),
  nrow = 8,
  ncol = 10,
  byrow = FALSE
)
print(m1[5,2])
print(m1[c(5:7),])
m2 <- m1[c(3:6),c(4:9)]
class(m2)
mode(m2)
```
The class of variable m2 is a matrix. Its mode is numeric.

Challenge 3:
```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```

Challenge 4:

1) Define superfamilies as character vectors

```{r}
Superfamily_Lorisoidea <- c("Lorisidae", "Galagidae")
Superfamily_Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Superfamily_Tarsioidea <- c("Tarsiidae")
Superfamily_Ceboidea <- c("Cebidae", "Atelidae", "Pitheciidae")
Superfamily_Hominoidea <- c("Hylobatidae", "Hominidae")
Superfamily_Cercopithecoidea <- c("Cercopithecidae")
```

2) Define Infraorders and Parvorders as lists of Superfamilies, name items accordingly
```{r}
Infraorder_Lorisiformes <- list(Superfamily_Lorisoidea)
names(Infraorder_Lorisiformes) <- c("Superfamily: Lorisoidea")
Infraorder_Lemuriformes <- list(Superfamily_Lemuroidea)
names(Infraorder_Lemuriformes) <- c("Superfamily: Lemuroidea")
Infraorder_Tarsiiformes <- list(Superfamily_Tarsioidea)
names(Infraorder_Tarsiiformes) <- c("Superfamily: Tarsioidea")
Parvorder_Platyrrhini <- list(Superfamily_Ceboidea)
names(Parvorder_Platyrrhini) <- c("Superfamily: Ceboidea")
Parvorder_Catarrhini <- list(Superfamily_Hominoidea, Superfamily_Cercopithecoidea)
names(Parvorder_Catarrhini) <- c("Superfamily: Hominoidea", "Superfamily: Cercopithecoidea")
Infraorder_Simiiformes <- list(Parvorder_Platyrrhini, Parvorder_Catarrhini)
names(Infraorder_Simiiformes) <- c("Parvorder: Platyrrhini", "Parvorder: Catarrhini")
```

3) Define Suborders as lists of Infraorders and Parvorders
```{r}
Suborder_Strepsirhini <- list(Infraorder_Lorisiformes, Infraorder_Lemuriformes)
names(Suborder_Strepsirhini) <- c("Infraorder: Lorisiformes", "Infraorder: Lemuriformes")
Suborder_Haplorhini <- list(Infraorder_Tarsiiformes, Infraorder_Simiiformes)
names(Suborder_Haplorhini) <- c("Infraorder: Tarsiiformes", "Infraoder: Simiiformes")
```

4) Define Order Primates as list of Suborders
```{r}
Order_Primates <- list(Suborder_Strepsirhini, Suborder_Haplorhini)
names(Order_Primates) <- c("Suborder: Strepsirhini", "Suborder: Haplorhini")
```

5) Create new variable for new world monkeys using double bracket notation. Class and mode are both list.
```{r}
nwm <- Order_Primates[[2]][[2]][1]
class(nwm)
mode(nwm)
```

6) Extract tarsiers using $
```{r}
Order_Primates$`Suborder: Haplorhini`$`Infraorder: Tarsiiformes`$`Superfamily: Tarsioidea`
```




